---
title: "Central Limit Theorem"
author: "Sachin Chavan"
date: "08/27/2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simulator to Demonstrate CLT

## Generate Population from Chi Square distribution
```{r}
chi_population <- rchisq(10000000,2)
hist(chi_population,main="Chi-square Distribution",xlab="Population Distribution")
print("Mean of the population")
mean(chi_population)
print("Standard Deviation of the population")
sd(chi_population)
```

## Distribution of sample means of size 50
```{r}
sample_50 <- sample(chi_population,50,replace=TRUE)
hist(sample_50,main="Indiviual Sample Distribution",xlab="Individual Sample")
print("Mean of the Sample")
mean(sample_50)
print("Standard Deviation of the Sample")
sd(sample_50)

```
## Data Holder
```{r}
simulations  <- 10000 # Sample of 50 taken 10000 times from population
xbar_holder  = numeric(simulations) # This will hold all the sample means for the first distribution.
```

## Simulate and Store
Generate 10000 samples each of size 50 and find the mean of each sample.  Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample <- sample(chi_population,50,replace=TRUE)
  xbar1 = mean(sample)
  xbar_holder[i] = xbar1
}
```

## display the distribution of sample means (plot a histogram of the sample means)
```{r}
par(mfrow = c(2,1))
hist(xbar_holder, col = "blue", main = paste("Distribution of the sample means: n = 50 and df=2"), xlab = "Dist Sample Means", xlim = c(-20,20))
```

## summary statistics of the distribution of the simulated sample means. 
```{r}
summary(xbar_holder) # number summary and the mean
print('Standard Deviation of sampling distribution')
sd(xbar_holder) # standard deviation of dstribuion
print('Standard Error')
sd(xbar_holder)*sqrt(50)
```


