---
title: "Beers_Analysis"
author: "Sachin Chavan"
date: "10/13/2019"
output: html_document
---

### Load follwing libraries

*  ggplot2 - visualizations
*  tidyverse
*  naniar and visdat - visualizations for missing data
*  mice - Imputation


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(naniar)
library(visdat)
library(GGally)
library(mice)  
library(VIM)
library(lattice)
library(maps)
library(treemapify)
```

### Load data into memory from csv 

*  Load Breweries from csv
*  Load Beers from csv 
*  Merge Breweries and Beers
*  Rename Names column after merging two datasets

```{r dpi=100}
breweries_ds <- read.csv('data/Breweries.csv',header = TRUE)
beers_ds     <- read.csv('data/Beers.csv'    ,header = TRUE)
bmerged_ds   <- merge(breweries_ds,beers_ds,by.x="Brew_ID",by.y="Brewery_id")
names(bmerged_ds)[2] <- "BreweryName"
names(bmerged_ds)[5] <- "BeerName"
```

### Structures of the datasets
* breweris_ds - Breweries in USA
* beers_ds    - Different beer styles with ABV and IBU

```{r}
str(breweries_ds)
str(beers_ds)
str(bmerged_ds)
```

### Summary Statistics of both datasets
* breweris_ds - Breweries in USA
* beers_ds    - Different beer styles with ABV and IBU

```{r}
summary(breweries_ds)
summary(beers_ds)
summary(bmerged_ds)
```

### Visual Summary
* Check distributions

```{r}


```

### Missing Values
* breweris_ds - Breweries in USA
* beers_ds    - Different beer styles with ABV and IBU

```{r}
vis_dat(breweries_ds,palette = "qual")
vis_dat(beers_ds,palette = "qual")
```


